How to Analyze Build Logs

### 2021-04-19 tse-paper/paper.tex
inccl. system log description feedback, remove snowballing term

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error.
\todo{cite bart paper?}
This
manual activity is tedious and prone to
errors~\citep{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\citep{beller2017oops} \todo{check, reviewer comment}, finding the small chunk
of information linked to the actual error, is akin to
searching for a needle in a haystack.
The large number of unrelated, but ambiguous
warnings which many build
logs regularly contain further compounds this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\citep{islam2017insights,seo2014programmers}, differentiate
testing practices~\citep{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\citep{ni2017cost,bisong2017built,haghighatkhah2018test,
machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs)
in CI
builds~\citep{zampetti2017open}.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.7\columnwidth, clip]{img/lit_mapping_svg2.pdf}
	\caption{Literature selection (following Petersen et
	al.~\citep{petersen2015guidelines}).}
	\label{fig:lit-mapping}
\end{figure}

@@

When analyzing system log files, the first goal is generally to
separate the constant and variable parts within a log
message~\citep{nagappan2010abstracting,he2017towards}.
Next, the log
messages are clustered into log events, unifying messages with
identical constant parts and varying parameters.
The output is an
ordered list of timed events and their corresponding parameter
values~\citep{he2016evaluation}.
This structured log can serve as
input to various machine learning and data mining processes.
Apart
from a large body of research on system logs, an equally mature amount
of commercial-grade and
open source tooling exists to analyze system logs---such as, for
example, Elasticsearch, Logstash and Kibana (the so-called ELK
stack)~\citep{sanjappa2017analysis,bajer2017building}.

@@

With these 256 remaining works, we followed a backward snowball
sampling for related work.
If a work referenced a new work in the context
of build log analysis, we added the new one to the literature set.
This added five works (eight before
duplicate elimination), leading to a total of 261
works.

>>>>

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error
~\citep{vassallo2019every}.
This manual activity is tedious and prone to
errors~\citep{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\citep{beller2017oops} \todo{check, reviewer comment}, finding the small chunk
of information linked to the actual error, is akin to
searching for a needle in a haystack.
The large number of unrelated, but ambiguous
warnings which many build
logs regularly contain further compounds this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\citep{islam2017insights,seo2014programmers}, differentiate
testing practices~\citep{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\citep{ni2017cost,bisong2017built,haghighatkhah2018test,
machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs)
in CI
builds~\citep{zampetti2017open}.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.7\columnwidth, clip]{img/lit_mapping.pdf}
	\caption{Literature selection (following Petersen et
	al.~\citep{petersen2015guidelines}).}
	\label{fig:lit-mapping}
\end{figure}

@@

Before system logs can be analyzed, the raw log data needs to be
abstracted into a structured
events list~\citep{el-masri2020a-systematic}.
The first step of this log abstraction is to define or discover
log message templates, e.g. by
separating the constant and variable parts within a log
message~\citep{nagappan2010abstracting,he2017towards}.
In the second step of the log abstraction, the log
messages are matched to the templates, unifying messages with
identical constant parts and varying parameters under the same event.
The output is an
ordered list of timed events and their corresponding parameter
values~\citep{he2016evaluation}.
This structured log can serve as
input to log analysis approaches based on, e.g.,
machine learning and data mining processes.
Apart
from a large body of research on system logs, an equally mature amount
of commercial-grade and
open source tooling exists to analyze system logs---such as, for
example, Elasticsearch, Logstash and Kibana (the so-called ELK
stack)~\citep{sanjappa2017analysis,bajer2017building}.

@@

If a work referenced a new work in the context
of build log analysis, we added the new one to the literature set.
This added five works (eight before
duplicate elimination), leading to a total of 261
works.
